InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-29 paper.tex
fixed citation
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI. In the training stage the detector tryed to differentiate between human and ai text while a paraphraser trained to make the text more humanly.
The Ai-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{RADAR}.

>>>>

The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI. In the training stage the detector tryed to differentiate between human and AI text while a paraphraser trained to make the text more human.
The Ai-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
